DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-07 Draft Ped Metrics Example.Rmd
adds public schools

#### Schools
```{r}
libraries <- community %>%
  filter(TYPE == "PUBLIC LIBRARY")

@@

@@

```{r plot_transit}
kitsap +
  geom_sf(data = transit_cp2, aes(fill = id), 
          lwd = 0, alpha = 0.3) +
  geom_sf(data = transit_cp, aes(color = 1), color = "black", show.legend = FALSE) +
  theme_void() +
  labs(title = 'Kitsap County Transit Centers and Transfer Points',
       subtitle = "Libraries not labeled with color are not in the unincorporated county",
       caption = "Data source: Kitsap Transit Website[@ktransit]",
       fill = "Transit Centers")

>>>>

#### Schools
```{r}
pub_schools <- schools %>%
  filter(TYPE == "PUBLIC")

pub_schools2 <- getWalkingPolygonInCounty(pub_schools, "NAME")
```

Kitsap County has `r nrow(pub_schools)` Public schools; however, only `r nrow(pub_schools2)` are outside of city limits. Here they are shown with a 30 minute walking distance.

```{r plot_pubschools}
kitsap +
  geom_sf(data = pub_schools2, aes(fill = id), 
          lwd = 0, alpha = 0.3) +
  geom_sf(data = pub_schools, aes(color = 1), color = "black", show.legend = FALSE) +
  theme_void() +
  labs(title = 'Kitsap County Public Schools',
       subtitle = "Schools not labeled with color are not in the unincorporated county",
       caption = "Data source: Kitsap GIS - data in development",
       fill = "Public Schools")

@@

```{r loop_pubschools,include=FALSE,echo=FALSE}
the_schools <- unique(st_set_geometry(pub_schools2, NULL)$id)
loop_df <- st_as_sf(pub_schools2) %>% mutate(tomatch = id)

score_breakdowns <- score_breakdowns %>%
  bind_rows(tibble(Area = the_schools, Score = NA))

expanded_child <- lapply(
    the_schools,
    function(x) {
      knitr::knit_expand(file = "child_single_geo.Rmd",
                                   current_geo = x )
    })

@@

```{r plot_transit}
kitsap +
  geom_sf(data = transit_cp2, aes(fill = id), 
          lwd = 0, alpha = 0.3) +
  geom_sf(data = transit_cp, aes(color = 1), color = "black", show.legend = FALSE) +
  theme_void() +
  labs(title = 'Kitsap County Transit Centers and Transfer Points',
       subtitle = "Centers not labeled with color are not in the unincorporated county",
       caption = "Data source: Kitsap Transit Website[@ktransit]",
       fill = "Transit Centers")
